Variana Reloaded

### 2022-11-16 papers/variana/notes.tex
Fall 2022 changes

@@

This requires evaluating both the current fit and the associated orthonormal basis functions at each sample point. Note that, in the canonical basis, we don't have to re-evaluate the basis functions on each iteration, but we have to re-evaluate the KL Hessian if we are to implement the genuine Newton method.

Once the moving coordinates are updated through $\hat{\nu}$, we convert them to canonical coordinates by left multiplying $\hat{\nu}$ by the above transition matrix.

>>>>

Let $\theta=T\nu$.

$$
\sqrt{Z}\theta_0 =
\nu_0
- \sum_i \frac{m_i}{s_i} \nu_{1i}
+ \frac{1}{\sqrt{2}} \sum_i \left(\frac{m_i^2}{s_i^2} - 1\right) \nu_{2i}
.
$$

$$
\sqrt{Z}\theta_{1i}
=
\frac{\nu_{1i}}{s_i} - \sqrt{2} \frac{m_i\nu_{2i}}{s_i^2}.
$$

$$
\sqrt{Z}\theta_{2i}
=
\frac{\nu_{2i}}{\sqrt{2}s_i^2}.
$$

@@

This requires evaluating both the current fit and the associated orthonormal basis functions at each sample point. Evaluating the basis function requires computing the natural parameters $(Z, m, s)$. Note that, in the canonical basis, we don't have to re-evaluate the basis functions on each iteration, but we have to re-evaluate the KL Hessian if we are to implement the genuine Newton method.

Once the moving coordinates are updated through $\hat{\nu}$, we convert them to canonical coordinates by left multiplying $\hat{\nu}$ by the above transition matrix, which gives us the increment $\delta\theta=T\hat{\nu}$ to add to the current $\theta$ estimate for the next iteration.
